Fractional land cover classification method assessment using PROBA-V satellite data

### 2019-07-24 article/article.tex
Upgrade to TexLive 2019

\added[id=dm]{
\textbf{Objectives}:
}

@@

\begin{table}
\centering
\begin{tabular}{llllll}
\toprule
\textbf{Model} & \textbf{\ac{RMSE} (\%)} & \textbf{\ac{MAE} (\%)} & \textbf{\acrshort{NSE}} & \textbf{\ac{OA} (\%)} & \textbf{Kappa} \\
\midrule
Intercept
& 30    &       &       & 25±4  & 0.1       \\
Fuzzy nearest centroid
& 22    &       &       & 49    & 0.41      \\
Neural networks
& 19.5  &       &       &       &           \\
PLS regression
& 19    &       &       & 47±5  & 0.36±0.07 \\
Logistic regression
& 18.7  & 9.8   &       & 66±4  & 0.57      \\
Lasso regression
& 18.5  &       &       &       &           \\
Random forest
& 16.6  & 9.2   & 0.67  & 68±4  & 0.60      \\
\ensuremath{''} histogram matched
& 22.0  & 9.7   & 0.43  & 66±2  & 0.58±0.03 \\
\ensuremath{''} two-step
& 18.3  & 8.0   & 0.59  & 72±2  & 0.63      \\
\ensuremath{''} three-step
& 18.6  & 8.2   & 0.59  & 71±4  & 0.64      \\
\ensuremath{''} \ensuremath{''} histogram matched
& 21.3  & 9.1   & 0.46  & 68±3  & 0.61      \\
\bottomrule
\end{tabular}
\caption{Accuracy statistics of the models tested.}
\label{tab-accuracy}
\end{table}

@@

\minisection{Author Contributions} DM JV NT MH ML

@@

\minisection{Acknowledgements} VITO

>>>>

Global land cover maps

\textbf{Objectives}:

@@

\begin{table}
\centering
\begin{tabular}{llllll}
\toprule
\textbf{Model} & \textbf{\ac{RMSE} (\%)} & \textbf{\ac{MAE} (\%)} & \textbf{\acrshort{NSE}} & \textbf{\ac{OA} (\%)} & \textbf{Kappa} \\
\midrule
Intercept
& 30.7  & 21.8  & 0     & 24±4  & 0.11±0.04 \\
Fuzzy nearest centroid
& 22    &       &       & 49    & 0.41      \\
Neural networks
& 19.5  &       &       &       &           \\
PLS regression
& 19    &       &       & 47±5  & 0.36±0.07 \\
Logistic regression
& 20.0  & 10.7  & 0.53  & 66±4  & 0.57      \\
Lasso regression
& 18.5  &       &       &       &           \\
Random forest
& 16.6  & 9.2   & 0.67  & 68±4  & 0.60      \\
\ensuremath{''} histogram matched
& 22.0  & 9.7   & 0.43  & 66±2  & 0.58±0.03 \\
\ensuremath{''} two-step
& 18.3  & 8.0   & 0.59  & 72±2  & 0.63      \\
\ensuremath{''} three-step
& 18.6  & 8.2   & 0.59  & 71±4  & 0.64      \\
\ensuremath{''} \ensuremath{''} histogram matched
& 21.3  & 9.1   & 0.46  & 68±3  & 0.61      \\
\bottomrule
\end{tabular}
\caption{Accuracy statistics of the models tested.}
\label{tab-accuracy}
\end{table}

@@

\minisection{Author Contributions} DM JV NT MH ML BK

@@

\minisection{Acknowledgements} VITO, time series group (BB)
